|

### 2022-06-15 appendix/appendix-short.Rmd
update paper and appendix

---
title: |
       | Supplementary Material for "Vigilantism, Institutions, and Honor Culture: Understanding Attitudes toward Lynching in Brazil"
author:
- "Danilo Freire[^freire]"
- "David Skarbek[^skarbek]"
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: ../article/references.bib
biblio-style: ../article/chicago-ff.bst
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    highlight: haddock
    toc: true
    toc_depth: 3
    keep_tex: no
    template: template.latex
---

@@

This appendix contains additional tables and graphs that complement the results
we present in "_Vigilantism, Institutions, and Honor Culture: Understanding
Attitudes towards Lynching in Brazil_". An extended version of this file, which
includes further tests for heterogeneous effects and `R` code, is available at
[_redacted for peer review_]. The repository also contains our pre-analysis
plan and the `php` scripts we used in our conjoint experiment.

>>>>

---
title: |
       | Supplementary Material for "Vigilantism and Institutions: Understanding Attitudes toward Lynching in Brazil"
author:
- "Danilo Freire[^freire]"
- "David Skarbek[^skarbek]"
date: 14 June 2022
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: ../article/references.bib
biblio-style: ../article/chicago-ff.bst
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    highlight: haddock
    toc: true
    toc_depth: 3
    keep_tex: no
    template: template.latex
---

@@

This appendix contains additional tables and graphs that complement the results
we present in "_Vigilantism and Institutions: Understanding Attitudes towards
Lynching in Brazil_". An extended version of this file, which includes further
tests for heterogeneous effects and `R` code, is available at [_redacted for
peer review_]. The repository also contains our pre-analysis plan and the `php`
scripts we used in our conjoint experiment.

### 2022-06-15 appendix/appendix.Rmd
update paper and appendix

---
title: |
       | Supplementary Materials for "Vigilantism, Institutions, and Culture: Understanding Attitudes towards Lynching in Brazil"
author:
- "Danilo Freire[^freire]"
- "David Skarbek[^skarbek]"
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: ../article/references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    highlight: haddock
    toc: true
    toc_depth: 3
    keep_tex: no
    template: template.latex
---

@@

@@

This appendix contains the `R` code required to replicate the results we
present in "_Vigilantism, Institutions, and Culture: Understanding Attitudes
towards Lynching in Brazil_". This file also includes the descriptive
statistics of our sample, the average marginal component effects (AMCEs) for
our conjoint experiment, and additional subgroup analyses for all three
experiments.

@@

# Models
m1 <- lm(exp01_outcomes ~ exp01_police_treat, data = df_exp01)
m2 <- lm(exp01_outcomes ~ exp01_slow_justice_treat, data = df_exp01)
m3 <- lm(exp01_outcomes ~ exp01_small_punishment_treat, data = df_exp01)
m4 <- lm(exp01_outcomes ~ exp01_any_treat, data = df_exp01)

# Table
stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4),
          p = starprep(m1, m2, m3, m4, stat = "p.value"),
          header = FALSE, align = TRUE, label = "tab:exp01main",
          title = "Experiment 01 -- Main Results", style = "apsr",
          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
          covariate.labels = c("Police does not patrol area", "Justice too slow",
                               "Punishment not harsh enough", "Combined treatments"),
          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
          keep.stat = "n", no.space = TRUE)
```
\normalsize

@@

Here we estimate the effect of gender, race, and political ideology on
lynching support. We find that males, blacks, and mixed race individuals are
more likely to endorse lynchings when compared to females and whites,
respectively. Left and center-left voters, in contrast, show lower support for
lynchings when compared to centrists.

\footnotesize
```{r exp01-baseline, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
df_exp01_group <- df_exp01 %>%
  filter(gender == c("Female", "Male"),
         race %in% c("Asian", "Black", "Mixed Race", "White"),
         ideology %in% c("Center", "Center-Left", "Center-Right",
                         "Left", "Right"))

m1 <- lm(exp01_outcomes ~ gender, data = df_exp01_group)
m2 <- lm(exp01_outcomes ~ relevel(race, ref = "White"), data = df_exp01_group)
m3 <- lm(exp01_outcomes ~ relevel(ideology, ref = "Center"), data = df_exp01_group)
m4 <- lm(exp01_outcomes ~ gender + relevel(race, ref = "White") +
         relevel(ideology, ref = "Center"), data = df_exp01_group)

stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4), p = starprep(m1, m2, m3, m4, stat = "p.value"),
          header = FALSE, align = TRUE, label = "tab:exp01baseline",
          title = "Experiment 01 -- Determinants of Baseline Levels of
          Lynching Support", style = "apsr", dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
          covariate.labels = c("Male", "Asian", "Black", "Mixed Race",
                               "Left", "Center-Left", "Center-Right", "Right"),
          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
          keep.stat = "n", no.space = TRUE)
```
\normalsize

@@

@@

\footnotesize
```{r conjoint-lda, warning=F, message=F, error=F, cache=T, fig.width=10, fig.height=9, fig.post="H"}
# Unsupervised LDA
tmod_lda <- textmodel_lda(dfmat, k = 3)
terms(tmod_lda, 10)
table(topics(tmod_lda))
```
\normalsize

Our last model is a semisupervised LDA, in which we include a series of
keywords to measure how frequently some pre-defined topics appear often in the
responses. We adopt a conservative approach and only include words that we have
a high degree of confidence that are not ambiguous. There are four pre-defined
topics in this estimation. The first refers to victims, and include the
Portuguese words for _children_, _life_, and _victim_ (along with possible
variations). The second topic describes crime characteristics with words such
as _murder_, _rape_, _kill_, _molest_, and _steal_. The next group has four
keywords that describe lynching perpetrators, and they are _gangs_, _family_,
_bystanders_, and _police_. The fourth topic includes terms to identify
respondents who are against lynchings, and we added _against_, _none_, _do not
agree_, and _choice_ as seed terms. We see that the topic describing crime
characteristics is the one that appears more often.

\footnotesize
```{r conjoint-seededlda, warning=F, message=F, error=F, cache=T, fig.width=15, fig.height=9, fig.pos="H"}
# Semisupervised LDA
keywords <- dictionary(list(victim      = c("crian*", "vida*", "v*tima*"),
                            crime       = c("assassin*", "estupr*", "mata*", "molest*", "roub*"),
                            perpetrator = c("gang*", "fam*lia*", "pedestr*", "pol*cia*"),
                            against     = c("contra", "escolha", "nenhum*", "n*o concord*", "op**o")))

@@

# Table
stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4), header = FALSE,
          p = starprep(m1, m2, m3, m4, stat = "p.value"), align = TRUE,
          title = "Experiment 03 -- Main Results", style = "apsr", label = "tab:exp03main",
          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
          covariate.labels = c("Constitution and penal code", "Human rights",
                               "Vendettas", "Combined treatments"),
          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
          keep.stat = "n", no.space = TRUE)
```
\normalsize

@@

>>>>

---
title: |
       | Supplementary Material for "Vigilantism and Institutions: Understanding Attitudes toward Lynching in Brazil"
author:
- "Danilo Freire[^freire]"
- "David Skarbek[^skarbek]"
date: 14 June 2022
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: ../article/references.bib
biblio-style: ../article/chicago-ff.bst
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    highlight: haddock
    toc: true
    toc_depth: 3
    keep_tex: no
    template: template.latex
---

@@

\appendix

@@

This appendix contains the `R` code required to replicate the results we
present in "_Vigilantism and Institutions: Understanding Attitudes towards
Lynching in Brazil_". This file also includes the descriptive statistics of our
sample, the average marginal component effects (AMCEs) for our conjoint
experiment, and additional subgroup analyses for all three experiments.

@@

m1 <- lm(exp01_outcomes ~ exp01_police_treat, data = df_exp01)
m2 <- lm(exp01_outcomes ~ exp01_slow_justice_treat, data = df_exp01)
m3 <- lm(exp01_outcomes ~ exp01_small_punishment_treat, data = df_exp01)
m4 <- lm(exp01_outcomes ~ exp01_any_treat, data = df_exp01)

stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4), p = starprep(m1, m2, m3, m4, stat = "p.value"),
          header = FALSE, align = TRUE, label = "tab:exp01main", title = "Experiment 01 -- Main Results",
          style = "apsr", dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
          covariate.labels = c("Police does not patrol area", "Justice too slow",
                               "Punishment not harsh enough", "Combined treatments"),
          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
          keep.stat = "n", no.space = TRUE)
```
\normalsize

@@

Here we estimate the effect of gender, race, and political ideology on lynching
support. We find that males are more likely to tolerate lynchings, whereas left
and center-left voters oppose lynchings more strongly than centrists. In our
second model, we find no effect for race, and in the last column we see that
white respondents are less supportive of lynchings.

\footnotesize
```{r exp01-baseline, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
df_exp01_group <- df_exp01 %>%
  filter(gender == c("Female", "Male"),
         race %in% c("Asian", "Black", "Mixed Race", "White"),
         ideology %in% c("Center", "Center-Left", "Center-Right", "Left", "Right")) %>%
  mutate(race = fct_relevel(race, "Black"), ideology = fct_relevel(ideology, "Center"))

df_exp01_gender <- df_exp01 %>% filter(gender == c("Female", "Male"))
df_exp01_race <- df_exp01 %>% filter(race %in% c("Asian", "Black", "Mixed Race", "White")) %>%
  mutate(race = fct_relevel(race, "Black"))
df_exp01_ideology <- df_exp01 %>%
         filter(ideology %in% c("Center", "Center-Left", "Center-Right", "Left", "Right")) %>%
         mutate(ideology = fct_relevel(ideology, "Center"))

m1 <- lm(exp01_outcomes ~ gender, data = df_exp01_gender)
m2 <- lm(exp01_outcomes ~ race, data = df_exp01_race)
m3 <- lm(exp01_outcomes ~ ideology, data = df_exp01_ideology)
m4 <- lm(exp01_outcomes ~ gender + race + ideology, data = df_exp01_group)

stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4), p = starprep(m1, m2, m3, m4, stat = "p.value"),
          header = FALSE, align = TRUE, label = "tab:exp01baseline",
          title = "Experiment 01 -- Determinants of Baseline Levels of
          Lynching Support", style = "apsr", dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
          covariate.labels = c("Male", "Asian", "Mixed Race", "White",
                               "Left", "Center-Left", "Center-Right", "Right"),
          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
          keep.stat = "n", no.space = TRUE)
```
\normalsize

@@

### Political Ideology

Here we disaggregate the results according to political ideology. We see that
political views do not change the overall responses.

\footnotesize
```{r conjoint-ideology, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.2, fig.pos="H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(ideology)
cjdt$Ideology <- factor(cjdt$ideology)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by =
            ~Ideology)

# Plot
plot(mm_by, group = "Ideology", vline = 0.5, header_fmt = "%s") +
  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
  scale_colour_viridis_d(option = "inferno", end = 0.8)

# Tables
mm_left <- mm_by %>% filter(BY == "Left")
table_mm_by(mm_left, capt = "Marginal Means -- Left")
mm_center_left <- mm_by %>% filter(BY == "Center-Left")
table_mm_by(mm_center_left, capt = "Marginal Means -- Center-Left")
mm_center <- mm_by %>% filter(BY == "Center")
table_mm_by(mm_center, capt = "Marginal Means -- Center")
mm_center_right <- mm_by %>% filter(BY == "Center-Right")
table_mm_by(mm_center_right, capt = "Marginal Means -- Center-Right")
mm_right <- mm_by %>% filter(BY == "Right")
table_mm_by(mm_right, capt = "Marginal Means -- Right")
mm_dont_know <- mm_by %>% filter(BY == "Don't Know")
table_mm_by(mm_dont_know, capt = "Marginal Means -- Don't Know")
mm_not_say <- mm_by %>% filter(BY == "Rather Not Say")
table_mm_by(mm_not_say, capt = "Marginal Means -- Rather Not Say")
```
\normalsize

@@

\footnotesize
```{r conjoint-lda, warning=F, message=F, error=F, cache=T, fig.width=10, fig.height=9, fig.post="H"}
# Unsupervized LDA
tmod_lda <- textmodel_lda(dfmat, k = 3)
terms(tmod_lda, 10)
table(topics(tmod_lda))
```
\normalsize

Our last model is a semisupervized LDA, in which we include a series of
keywords to measure how frequently some pre-defined topics appear often in the
responses. We adopt a conservative approach and only include words that we have
a high degree of confidence that are not ambiguous. There are four pre-defined
topics in this estimation. The first refers to victims, and include the
Portuguese words for _children_, _life_, and _victim_ (along with possible
variations). The second topic describes crime characteristics with words such
as _murder_, _rape_, _kill_, _molest_, and _steal_. The next group has four
keywords that describe lynching perpetrators, and they are _gangs_, _family_,
_bystanders_, and _police_. The fourth topic includes terms to identify
respondents who are against lynchings, and we added _against_, _none_, _do not
agree_, and _choice_ as seed terms. We see that the topic describing crime
characteristics is the one that appears more often.

\footnotesize
```{r conjoint-seededlda, warning=F, message=F, error=F, cache=T, fig.width=15, fig.height=9, fig.pos="H"}
# Semisupervized LDA
keywords <- dictionary(list(victim      = c("crian*", "vida*", "v*tima*"),
                            crime       = c("assassin*", "estupr*", "mata*", "molest*", "roub*"),
                            perpetrator = c("gang*", "fam*lia*", "pedestr*", "pol*cia*"),
                            against     = c("contra", "escolha", "nenhum*", "n*o concord*", "op**o")))

@@

stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4), header = FALSE,
          p = starprep(m1, m2, m3, m4, stat = "p.value"), align = TRUE,
          title = "Experiment 03 -- Main Results", style = "apsr", label = "tab:exp03main",
          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
          covariate.labels = c("Constitution and penal code", "Human rights",
                               "Vendettas", "Combined treatments"),
          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
          keep.stat = "n", no.space = TRUE)

```
\normalsize

As we did in the first experiment, we evaluate how individual characteristics
impact lynching support. The results are similar to those presented in table
\ref{tab:exp01baseline}, with the exception that the coefficient for white
respondents is negative in two estimations, and the coefficient for male does
not reach statistical significance in the last model ($p$-value = 0.11).

\footnotesize
```{r exp03-baseline, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
df_exp03_group <- df_exp03 %>%
  filter(gender == c("Female", "Male"),
         race %in% c("Asian", "Black", "Mixed Race", "White"),
         ideology %in% c("Center", "Center-Left", "Center-Right", "Left", "Right")) %>%
  mutate(race = fct_relevel(race, "Black"), ideology = fct_relevel(ideology, "Center"))

df_exp03_gender <- df_exp03 %>% filter(gender == c("Female", "Male"))
df_exp03_race <- df_exp03 %>% filter(race %in% c("Asian", "Black", "Mixed Race", "White")) %>%
  mutate(race = fct_relevel(race, "Black"))
df_exp03_ideology <- df_exp03 %>%
         filter(ideology %in% c("Center", "Center-Left", "Center-Right", "Left", "Right")) %>%
         mutate(ideology = fct_relevel(ideology, "Center"))

m1 <- lm(exp03_outcomes ~ gender, data = df_exp03_gender)
m2 <- lm(exp03_outcomes ~ race, data = df_exp03_race)
m3 <- lm(exp03_outcomes ~ ideology, data = df_exp03_ideology)
m4 <- lm(exp03_outcomes ~ gender + race + ideology, data = df_exp03_group)

stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4), p = starprep(m1, m2, m3, m4, stat = "p.value"),
          header = FALSE, align = TRUE, label = "tab:exp03baseline",
          title = "Experiment 01 -- Determinants of Baseline Levels of
          Lynching Support", style = "apsr", dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
          covariate.labels = c("Male", "Asian", "Mixed Race", "White",
                               "Left", "Center-Left", "Center-Right", "Right"),
          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
          keep.stat = "n", no.space = TRUE)
```
\normalsize

@@

# Ethics Statement

We adhered to the ethical guidelines provided by the Institutional Review Board
at Brown University and APSA's Principles and Guidance. To facilitate
transparency, we comment here on a few aspects of our research design. First,
we worked with the Brown University IRB to reduce the risk of harm for
participants taking the survey. This included consultation with a cultural
expert to inform the phrasing of the survey. Second, respondents received
compensation via Qualtrics, which paid respondents directly after they completed
the questionnaire. Each subject in Qualtrics' online panel received the
equivalent of 2.5 USD in Brazilian Reals (local currency). Respondents who do
not finish the survey will not receive compensation. The compensation is
appropriate for the participant population. As of August 17, 2020, Brazil's
monthly minimum wage is BRL1039, which amounts to 191 US dollars. Assuming 40
working hours per week, the hourly minimum wage equals 1.19 US dollars. Our
survey takes about 20 minutes to complete and respondents received 2.5 USD,
therefore subjects will receive a monetary compensation that is 6 times higher
than the local minimum wage. Third, we do not see any potential or perceived
conflicts of interest in carrying out this research. We received a grant of
$10,000 to conduct this research from the Centre for the Study of Governance &
Society at King’s College London, which receives support from the Templeton
Foundation. We are aware of no conflicts of interest from either source. All of
the code and data will be made publicly available.
